Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Comment out authors.
I think we also need to do the ISCI and LBL stuff.
Top-to-bottom proofreading.

\author{David Fifield, Chang Lan}
\author{
\IEEEauthorblockN{David Fifield and Chang Lan}
\IEEEauthorblockA{University of California, Berkeley}
}

@@

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names at different communication layers.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google's infrastructure,
that ignore the outside of an HTTPS request
and dispatch it internally according to the Host header.
The effect is that a user may communicate with any domain within the web service,
while appearing to communicate with any other domain.
If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
then blocking circumvention traffic means blocking the whole web service,
with resulting expensive collateral damage.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Communication with it is enabled through domain fronting.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
but which actually arrive at a special web server on a Tor relay.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
but there are other, more subtle considerations.
We describe what we have done to disguise other traffic ``tells'' in \meek,
such as using a real web browser to make HTTPS requests
for a believable TLS fingerprint.
We argue that these measures increase the censor's effort
beyond simple one-shot techniques such as IP address blocking, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

What we as circumventors have in our favor is the censor's
distaste for ``collateral damage,''
accidental overblocking committed in the course of trying to censor something else.
One way to win against the censor is to entangle circumvention traffic
with ordinary Internet traffic in a way that both must be blocked together
or not at all.
If the ordinary traffic is important enough,
above the censor's tolerance for overblocking,
then the circumvention traffic will get through.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high--collateral damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
See Section~\ref{sec:survey} for a listing of some suitable services.
Domain fronting can be used as a means of tunneling traffic
to a general-purpose proxy,
so it is not limited to HTTPS, nor to the domains of any specific web service.

The key idea of domain fronting is using
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
the DNS query,
the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
and the HTTP Host header~\cite[Section~14.23]{rfc2616}.
Normally, the same domain name appears in all three places.
In a domain-fronted request,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from censor by HTTPS encryption,
has a different name (the actual destination).

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers of communication.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor but meaningful to the CDN or web service,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

Neither the DNS nor the SNI can be blocked without
collaterally blocking the front domain.
The Host header is unknown to the censor,
but known to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

A Wget command shows domain fronting in action
on Google's infrastructure.
An HTTPS request for \urll{www.google.com} has a Host header for
\urll{maps.google.com}, and the HTML in the response is that of Google Maps.

@@

Domain fronting works with CDNs because a CDN's frontend server
(called an ``edge server''),
on receiving a request for a resource not already cached,
forwards the request to the domain in the Host header
(the ``origin server'').
(There are other ways for CDNs to work, but this ``origin pull''
configuration is common.)
% The certificate you get may be that of the front domain,
% or may be a generic shared domain.~\cite{httpsincdn}
The CDN's edge server won't forward requests just anywhere---it
has to be to the domain of a customer.
This means that in order to host a proxy,
one has to create an account and pay for bandwidth.
Fronting works with Google because Google App Engine, a web application platform,
can host a simple ``reflector'' application that emulates
an origin-pull CDN, simply forwarding every request to an origin server.

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI extension.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using an old browser that doesn't support SNI.
Domainless fronting can be useful when there is no front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address,
blocking requests without SNI,
or finding some other, presumably more expensive, test to distinguish
circumvention traffic.

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a Tor pluggable transport~\cite{pt}.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into a local Tor relay.
Downstream data received from the Tor relay
are returned to the client as HTTP responses
through the same fronted channel.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes its workings in detail.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has seen use by a small number of users.
Our deployment uses Google App Engine,
with the hidden actual domain \urll{meek-reflect.appspot.com}
hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other systems \meek\ can work with
and other deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now in use by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for \meek\ is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
with samples of HTTPS traffic at an Internet router.

To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy's rendezvous are the most direct
inspirations of this work.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
A savvy censor will use both means of censorship---therefore
effective circumvention requires countering both.

To the above challenges we may add a related one, active probing.
An active-probing censor does not merely passively observe traffic;
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
If the connection is successful, the server can then be blacklisted.
Active probing is a precise means of identifying a server as belonging to a circumvention system,
even when a protocol is hard to classify on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing followup scans to observed client connections to see
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},

There are two general strategies for countering DPI.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Well-traveled look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
They both work by superenciphering a stream, using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send anything
until the client proves knowledge of shared secret, depriving the censor
of an easy distinguisher.
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

The other strategy against DPI is the steganographic approach: look like
something the censor doesn't block.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP,
in order to match a firewall's whitelist.
StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy, which decodes it and forwards it to the destination.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

@@

The other grand challenge of proxy-based circumvention is address-based blocking.
Tor has long faced the blocking of its entry relays,
the addresses of which are in a public directory.
In response, Tor began to reserve a portion of its
new relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes bridge addresses
so that anyone can learn a few bridges, but it is hard to learn all of them.
BridgeDB uses captchas and other rate-limiting measures,
and over short time periods,
always returns the same set of bridges to the same requester,
preventing enumeration by simple repeated querying.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (obfs3 or ScrambleSuit);
the combination
of careful bridge address dispersal and obfuscated protocols
gives Tor's system a realistic claim to addressing both main challenges of circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data...},
where ``\textsl{data...}'' is the message the client wishes to send,
embedded in the URL.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
the web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.

Decoy routing~\cite{decoyrouting}, also called end-to-middle proxying,
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that lie
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing;
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a web service's frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it doesn't require knowing cooperation by network intermediaries.

@@

CensorSpoofer~\cite{censorspoofer}
decouples upstream and downstream data channels.
The client sends data to a CensorSpoofer proxy over a low-bandwidth covert channel such as email.
The proxy sends data back over a UDP channel, all the time
spoofing its source address so the packets appear to originate from some other ``dummy'' host.
The censor has no IP address to block, because the proxy's true address never appears on the wire.
Client and server have the challenge of agreeing on a dependable covert upstream channel
that must itself remain unblocked,
and the client must carry on a believable UDP conversation with the dummy host
(the authors suggest a VoIP call).

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path rather than the Host header.
For example, in an example S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
the censor only gets to ``see'' the generic domain part, \urll{s3.amazonaws.com}.
The path component \urll{/bucketname/filename},
which would reveal that CloudTransport is being used,
cannot be used for blocking because it is encrypted in HTTPS.

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of App
Engine and Host header--based domain fronting.
Traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
and the contents of all communications are revealed to App Engine.
Users of GoAgent upload their own personal copy of the proxy code to App Engine,
which is free of charge as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

>>>>

% ANON
% \author{David Fifield, Chang Lan}
% \author{
% \IEEEauthorblockN{David Fifield and Chang Lan}
% \IEEEauthorblockA{University of California, Berkeley}
% }

@@

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Domain fronting enables communication that is apparently with an allowed domain,
but actually with a forbidden domain.
The key idea is the use of different domain names at different communication layers.
One domain is used on the ``outside'' of an HTTPS request---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google,
that enable fronting by ignoring the outside of an HTTPS request
and dispatching it internally according to the Host header.
The effect of fronting is that a user may communicate with one domain,
even one forbidden by the censor,
while appearing to communicate with another.
If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
then blocking circumvention traffic means blocking the whole web service,
with resulting expensive collateral damage.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
but there are other, more subtle considerations.
We describe what we have done to disguise other traffic ``tells'' in \meek,
such as using a real web browser to make HTTPS requests
for a believable TLS fingerprint.
We argue that these measures increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blocking, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

What we as circumventors have in our favor is the censor's
distaste for ``collateral damage,''
accidental overblocking committed in the course of trying to censor something else.
One way to win against censorship is to entangle circumvention traffic
with ordinary Internet traffic in a way that either both must be blocked together,
or not at all.
If the ordinary traffic is important enough,
above the censor's tolerance for overblocking,
then the circumvention traffic will get through.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high--collateral damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
See Section~\ref{sec:survey} for a list of suitable services.
Domain fronting can be used to tunnel traffic
to a general-purpose proxy,
so that circumvention is not limited to HTTPS, nor to the domains of any specific web service.

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
the TLS Server Name Indication (SNI) extension~\cite[Section~3]{rfc6066},
and the HTTP Host header~\cite[Section~14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
But in a domain-fronted request,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from censor by HTTPS encryption,
carries another (the actual destination).

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers of communication.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor but meaningful to the intermediate web service,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

Neither the DNS request nor the SNI can be blocked without
collaterally blocking the front domain.
The Host header is invisible to the censor,
but visible to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

A Wget command shows domain fronting in action
on Google's infrastructure.
Here, an HTTPS request for \urll{www.google.com} has a Host header for
\urll{maps.google.com}. The HTML in the response is that of Google Maps.

@@

Domain fronting works with CDNs because a CDN's frontend server
(called an ``edge server''),
on receiving a request for a resource not already cached,
forwards the request to the domain in the Host header
(the ``origin server'').
(There are other ways for CDNs to work, but this ``origin pull''
configuration is common.)
% The certificate you get may be that of the front domain,
% or may be a generic shared domain.~\cite{httpsincdn}
Fronting works with Google because Google App Engine, a web application platform,
can host a simple ``reflector'' application that emulates
an origin-pull CDN, simply forwarding every request to an origin server.
In both cases, the intermediate web service does not forward requests just anywhere---it
has to be to the domain of a customer.
In order to run a fronting backend,
one has to create an account and pay for bandwidth.

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI extension.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using a web client that doesn't support SNI.
Domainless fronting can be useful when there is no front domain
known to have sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address,
blocking requests without SNI,
or finding some other, presumably more expensive, test to try to distinguish
circumvention traffic.

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received from Tor
are returned to the client as HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet length distribution
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy are the systems that most directly
inspire this work.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents of the communication may be.
A savvy censor will use both means of censorship, and
effective circumvention requires countering both.

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
If the connection is successful, the server may be blacklisted.
Active probing is a precise means of identifying whether a server as belongs to a circumvention system,
even when a protocol is hard to classify on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream,
good examples of which are
obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
Both obfs2 and obfs3 work by superenciphering an underlying stream,
using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
payload obfuscation, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send a reply
until the client proves knowledge of a shared secret.
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

The other strategy against DPI is the steganographic one: look like
something the censor doesn't block.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP,
in order to match a firewall's whitelist.
StegoTorus~\cite{stegotorus}
transforms traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

@@

The other grand challenge of proxy-based circumvention is address-based blocking.
Tor has long faced the problem of the blocking of its entry relays,
the addresses of which appear in a public directory.
In response, Tor began to reserve a portion of its
new relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes bridge addresses
so that anyone can learn a few bridges, but it is hard to learn all of them.
BridgeDB uses captchas and other rate-limiting measures,
and over short time periods,
always returns the same set of bridges to the same requester,
preventing enumeration by simple repeated querying.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (obfs3 or ScrambleSuit);
the combination
of careful bridge address distribution and obfuscated protocols
gives Tor's system a realistic claim to addressing both main challenges of circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

CensorSpoofer~\cite{censorspoofer}
decouples upstream and downstream data channels.
The client sends data to a CensorSpoofer proxy over a low-bandwidth covert channel such as email.
The proxy sends data back over a UDP channel, all the time
spoofing its source address so the packets appear to originate from some other ``dummy'' host.
The censor has no IP address to block, because the proxy's true address never appears on the wire.
Client and server have the challenge of agreeing on a dependable covert upstream channel
that must remain unblocked,
and the client must carry on a believable UDP conversation with the dummy host
(the authors suggest a VoIP call).

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data...},
where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.

Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that lie
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it doesn't require knowing cooperation by network intermediaries.

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path component of the URL.
For example, in an example S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
the censor only gets to ``see'' the generic domain part, \urll{s3.amazonaws.com}.
The path component \urll{/bucketname/filename},
which would reveal that CloudTransport is being used,
cannot be used for blocking because it is encrypted inside HTTPS.

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

Cloud-Entry~\cite{cloud-entry} is somewhat similar to GoAgent.
It also uses App Engine, but uses a socket API rather than a URL fetch API,
in order to support protocols other than HTTP and HTTPS.
Cloud-Entry has the same problem with NAT that flash proxy does,
because the proxy tries to connect back to the client with a socket.
App Engine kills web requests (and their associated socket connections)
that take longer than 60~seconds,
so users must reconnect at least that often.
